Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-01-30 tacl.tex
Make Figure 1 bigger-font (and smaller in size)
LArge-scale edits, primarily to Methodology

Work based on collocation measures often assumes a small, fixed set of part-of-speech (``POS'') combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering a full range of lexicalized multiword units. Relaxing this restriction, however, requires dealing with extreme overgeneration -- a central challenge is how to avoid redundancy when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of some partial correspondence with a true multiword lexical item. The former can be addressed to some extent using a syntax-sensitive association measure \cite{Brooke15b}, but addressing the latter properly requires an iterative model, where $n$-grams types in essence compete with each other to form a compact, parsimonious vocabulary which best explains the statistics extracted from the corpus. We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.

@@

\begin{figure}[!t]
\center{\includegraphics[width=0.35\textwidth]{FS_diagram_1.pdf}}
\caption{Multiword Terminology}
\label{fig:terminology}
\end{figure}

@@

Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb-noun combinations \cite{Fazly09}. The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.

@@

Our approach to FS identification involves optimization of the total explanatory power of a lattice where each node corresponds to an $n$-gram type. The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS). The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.  Given these relationships, we by iterating over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.

@@

The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage. An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names. 
Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams. The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
% TJB: added citation and removed "this is confirmed by empirical analysis" as it begs details of the specific analysis, which I think is more of a distraction than anything else at this point
In a POS-tagged corpus, potential gaps can be identified by a POS regular expression. This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus.  Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold. 
% TJB: this last sentence is a bit opaque
%=======
% In a POS-tagged corpus, potential gaps can be identified by a POS regular expression. This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus.  Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $(i+1)$-grams which are also over the threshold. 
%>>>>>>> origin/master

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected. LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}

\noindent
where $w_{j,k}$ as predictive context should be understood as not containing $w_{i}$ (similarly for $t_{j,k}$). 
% TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation

%These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts. 
% TJB: removed; seems to state the obvious
We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics. Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result. 
% TJB: is this a good thing or bad thing? slight lack of clarity here
It also ensures that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1.

In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (``\minLPR''):
\begin{displaymath}
\minLPR(w_{1,n}) = \min_{1 \leq i \leq n }{\LPR(w_i,w_{1,n})}
\end{displaymath}
The use of minimum here should be understood in the context of competition between nodes in the lattice: minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which an $n$-gram holds together, instead it focuses on the word which is its weakest link. For example, in the case we are evaluating the quality of \ex{be keep \gap under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.

@@

The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of maximizing the overall explanatory power of the lattice. Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained. We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on. When a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence. When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged. Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it is off. The base value of $E_{0}$ is the inverse of minLPR: when the minLPR metric is 1, corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1. The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS. There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.

We weight these functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it. We define $E_0$, then, as minLPR to the negative power of some as yet undefined non-negative function $d_0$:
\begin{displaymath}
E_0(t) = \minLPR(t)^{-d_0(t)}
\end{displaymath}
and $E_1$ is the cost parameter $C$ to the negative power of an analogous non-negative function $d_1$:
\begin{displaymath}
E_1(t) = C^{-d_1(t)}
\end{displaymath}
The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.

\begin{figure*}[!tb]
\center{\includegraphics[width=0.8\textwidth]{FS_diagram_2.pdf}}
\caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
\label{fig:example}
\end{figure*}

@@

The $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance, be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}. These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS). A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).

@@

The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice. Our model includes two types of covering: hard and soft. \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other: In \figref{fig:example}, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one. We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.  We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR ratios \cite{Brooke15b}. In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that corresponds to occurrences of \ex{keep \gap under wraps}. This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}\Big)
\end{displaymath}
This equation is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.

@@

A simple but effective solution which avoids introducing parameters makes use of the minLPR values of the relevant nodes. In the most common (two node) situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher, which greatly restricts its effect. Generalized to consider the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$. We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.

@@

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. Though there are exceptions, it is generally the case that independent formulaic sequences do not overlap. For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both have high minLPR. To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of having turned-off nodes, we decrease the explainedness of the turned-on nodes, which serves to express confusion at having overlapping FS. The idea behind covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but for overlaps a penalty is a more appropriate mechanism. Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$. We define $d_1(t)$, the exponential term for the $E_1(t)$, as:
\begin{displaymath}
	d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(o_i)}}
\end{displaymath}

@@

The dependence of the explainedness of nodes on their neighbors as discussed in the preceding section effectively prohibits a global optimization of the lattice. Fortunately, though most of the nodes in the lattice are part of a single main connected component, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we perform this has an effect on the result: among the obvious options, good results are obtained when ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.

Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node. If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated. Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to the status of the node under consideration whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.  Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.

In practice, we apply the following restrictions, which significantly reduce the runtime without sacrificing the quality of the output lexicon (based on development set testing):
\begin{compactitem}
\item We limit the total number of relevant nodes to 5. When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation;
\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice;
\item Many nodes have a minLPR which is a little larger than 1. There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with a minLPR of less than 2.
\end{compactitem}

 \begin{center}
  \caption{ Statistics for test sets}
	 \label{tab:stats}
	 \begin{tabular}{lccccc}

       \hline
			& Contiguous FS & Contiguous non-FS & Gapped FS & Gapped non-FS & Fleiss Kappa\\
			 \hline
			ICWSM & 169 & 702 & 29 & 916& 0.84 \\
			BNC & 49 & 403 & 8 & 475 & 0.84 \\
			Croatian & 64 & 382 & 11 & 456 & 0.87 \\
			Japanese & 124 & 286 & 36 & 341 & 0.81\\
       \hline
 \end{tabular}

>>>>

Work based on collocation measures tends to assume a small, fixed set of part-of-speech (``POS'') combinations with higher productivity \cite{Evert:Krenn:2001,Pecina10} as a means of reducing overgeneration, with the obvious disadvantage of impeding the generation of a broad-coverage multiword lexicon. This is the central challenge addressed in this paper: how to avoid redundancy/computational intractability when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of partial correspondence with a true multiword lexical item. Our solution to this challenge takes the form of an iterative model, where $n$-gram types compete with each other in a lattice to generate a compact, parsimonious vocabulary which best explains the statistics extracted from the corpus. We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.

@@

\begin{figure}[!t]
\caption{Multiword Terminology}
\center{\includegraphics[width=0.3\textwidth]{FS_diagram_1.pdf}}
\label{fig:terminology}
\end{figure}

@@

Other research in MWEs has tended to be rather focused on particular syntactic patterns such as verb-noun combinations \cite{Fazly09}. The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model. Schneider et \al make use of existing manual lexical resources and note that an (unsupervised) automatic lexical resource could be useful addition to the model, although attempts to do so have achieved mixed success \cite{Riedl16}.

@@

Our approach to FS identification involves optimization of the total explanatory power of a lattice, where each node corresponds to an $n$-gram type. The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS). The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.  Given these relationships, we iterate over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.

@@

The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage. An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.} 
Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgement of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English and German \cite{Dehe:2002,Ludeling:2001}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}. Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold. As long as the count threshold  is significantly above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected. LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}
where $w_{j,k}$ denotes the word sequence $w_j,..., w_{i-1}, w_{i+1}, ..., w_{k}$ excluding $w_{i}$ (similarly for $t_{j,k}$). Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1.

We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics. %Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result. 
% TJB: I still find this confusing, given that we haven't formally introduced the lattice at this point; suggest leaving it out

In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (``\minLPR''):
\begin{displaymath}
\minLPR(w_{1,n}) = \min_{1 \leq i \leq n }{\LPR(w_i,w_{1,n})}
\end{displaymath}
Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link. For example, in the case of \ex{be keep \gap under},\footnote{Recall that our method involves lemmatization, in keeping with which all examples will be presented pre-lemmatized.} a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.

@@

The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of maximizing the overall explanatory power of the lattice. Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained. We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on. When a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence. When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.

Let $E_{1}$ be the explainedness of a node when it is on (corresponding to an $n$-gram which has been identified as an FS), and $E_{0}$ be the explainedness of a node when it is off. We calculate $E_{0}$ based on the inverse of minLPR: 
\begin{displaymath}
E_0(t) = \minLPR(t)^{-d_0(t)}
\end{displaymath}
and $E_{1}$ based on the inverse of a cost parameter $C$:
\begin{displaymath}
E_1(t) = C^{-d_1(t)}
\end{displaymath}
where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context, as detailed in the next section. When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$. $E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS. There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ to perform best across the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.

% The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.

\begin{figure}[!tb]
\caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
\center{\includegraphics[width=0.5\textwidth]{FS_diagram_2.pdf}}
\label{fig:example}
\end{figure}

@@

The $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume. For example, as detailed in \figref{fig:example}, the (gapped) $n$-gram \ex{keep \gap under wraps} would be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}. These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS). A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).

@@

The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice. Our model includes two types of covering: hard and soft. \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other. In \figref{fig:example}, \eg, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one. We do this by permanently disabling any covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.  We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR values \cite{Brooke15b}. In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}. This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}\Big)
\end{displaymath}
This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.

@@

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$. We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.

@@

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. In general, independent formulaic sequences do not predictably overlap. For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR. To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of having turned-off nodes, we decrease the explainedness of the turned-on nodes, which serves to express confusion at having overlapping FS. The idea behind covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but for overlaps a penalty is a more appropriate mechanism. Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$. We define $d_1(t)$, the exponential term for $E_1(t)$, as:
\begin{displaymath}
	d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(o_i)}}
\end{displaymath}

@@

The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice. Fortunately, though most of the nodes in the lattice are part of a single main connected component, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.

Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node on. If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated. Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration, whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.  Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.

In practice, we apply the following efficiency restrictions, which significantly reduce the runtime without sacrificing quality (based on development set testing):
\begin{compactitem}
\item We limit the total number of relevant nodes to 5. When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation;
\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice;
\item Many nodes have a minLPR which is a little larger than 1. There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with $\minLPR < 2$.
\end{compactitem}

\section{Evaluation}
\label{sec:evaluation}

We evaluate our approach across three different languages including evaluation sets derived from four different corpora. In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM blog corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}. To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus. Lemmatization included removing all inflectional marking from both words and POS tags. For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum of 4 words.

 \begin{center}
  \caption{ Statistics for test sets (``Cont'' = contiguous; ``Gap'' = gapped)}
	 \label{tab:stats}
	 \begin{tabular}{lc@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c}
